Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy

### 2018-08-08 draft/fmt.tex
simplify format

\documentclass[final,5p,times,onecolumn]{elsarticle}
%\documentclass[]{elsarticle}
\usepackage[labelfont=bf,justification=raggedright]{caption}
\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
%\documentclass[final,5p,times,twocolumn]{elsarticle}
\setlength{\mathindent}{3cm}
%Function format
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

@@

	%% Harvard
\bibliographystyle{elsarticle-num.bst}
\modulolinenumbers[5]
\journal{Materials and Design}
%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frontmatter}
\title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
%\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
%% Group authors per affiliation:
%\author{Maomao Wang\fnref{myfootnote}}

\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
\begin{abstract}
 The fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects. Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
\end{abstract}
\begin{keyword}
$\alpha$+$\gamma$ two phase TiAl alloy; void; molecular dynamics
\end{keyword}
\end{frontmatter}
\linenumbers

@@

\begin{table}[h]
	\centering
	\caption{Parameters of  nanocrystalline}

@@

\subsection{Atomic potential}
The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method, due to is better accuracy in metal lattice compare with F-S and L/J \cite{}. The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study, which is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}. We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.

>>>>

\documentclass[preview,times]{elsarticle}
\usepackage{lineno,hyperref}
\modulolinenumbers[5]
%\usepackage[labelfont=bf,justification=raggedright]{caption}
%\captionsetup[figure]{name=Fig. ,labelsep=period,singlelinecheck=true,skip=5pt}
%\captionsetup[table]{labelsep=newline,font=footnotesize,singlelinecheck=false,skip=5pt}
\linenumbers

%\documentclass[final,5p,times,twocolumn]{elsarticle}
%\setlength{\mathindent}{3cm}
%Function format
%\usepackage{lineno,hyperref}
%\modulolinenumbers[5]

@@

	%% Harvard
\bibliographystyle{elsarticle-num.bst}
%\modulolinenumbers[5]
\journal{Materials and Design}
%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frontmatter}
\title{Effect of Nanovoid on Fracture Process of Two-Phase $\alpha$($\rm TiAl$)+$\gamma$($\rm Ti_3Al$) Alloy}
%\tnotetext[mytitlenote]{*** \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}
%% Group authors per affiliation:
%\author{Maomao Wang\fnref{myfootnote}}

\address[mymainaddress]{School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China}
\begin{abstract}
 The fracture processes of nanocrystalline metallic materia is affected by dislocation, nanovoid and other defects. Existing studies of defect evolution in titanium-aluminium alloy cover the case that voids located in single crystals, inside grain in poly crystals and at the grain boundaries.Molecular dynamics simulation was performed to study the evolution of a spherical nanovoid in $\alpha$+$\gamma$ two-phase titanium-aluminium alloy under uniaxial tension.
\end{abstract}
\begin{keyword}
$\alpha$+$\gamma$ two phase TiAl alloy; void; molecular dynamics
\end{keyword}
\end{frontmatter}
%\linenumbers

@@

\begin{table}[ht]
\centering
\caption{Parameters of  nanocrystalline}

@@

\subsection{Atomic Potential}
The interaction of particle in the material is determined by interatomic potential. Many reported examples of crack propagation in metal materials were performed with embedded atomic method due to is better accuracy in metal lattice compare with F-S and L/J \cite{}. The embedded atom method (MEAM) potential developed by Zope and Mishin by \cite{} was used in the study. The simulation is submitted by MD simulations with the Large-scale Atomic/Molecular Massively Parallel Simulator (LAMMPS) open-source code \cite{}. We performed constant-pressure and constant-temperature(NPT) molecular dynamics simulation.
